Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-21 tex/main/manuscript.tex
结果第二段改完

% 另一方面，P2-P3，持续变化的水资源利用倾向与格局
On the other hand, as the most positive contributors to the IWRU index in P2 and P3, separately, 
tendentiousness (Figure~\ref{fig:dimensions}B and Figure~\ref{fig:dimensions}E) and patterns (Figure~\ref{fig:dimensions}C and Figure~\ref{fig:dimensions}F) of water utilization were enlarging their impacts. 
% 首先是用水比例的变化
Representing tendentiousness of water utilization, 
increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, 
while the influence of both is waning.
% 再讨论用水格局的变化
However, patterns of water utilization, with accelerating changes and larger contributions to the IWRU, 
were mainly benefited from the convergence of development paces between regions and the basin-wide intersectoral water balance.
% 最后，每个阶段起
In summary, the changes in various aspects of the water use characteristics of the Yellow River Basin over the past 60 years 
are reflected in the changes in the corresponding indicators of the three dimensions.

>>>>

% 另一方面，P2-P3，持续变化的水资源利用倾向与格局
On the other hand, as the most positive contributors to the IWRU index in P2 and P3 separately, tendentiousness and patterns of water utilization were keeping to enlarge their impacts (Figure~\ref{fig:dimensions}B and Figure~\ref{fig:dimensions}C). 
% 首先是用水比例的变化
Representing tendentiousness of water utilization, increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, while the influence of both are weakening (Figure~\ref{fig:dimensions}E).
% 再讨论用水格局的变化
However, patterns of water utilization, whose contributions to the IWRU are increasing, were mainly benefited from decreasing disparities in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).
